\documentclass{beamer}
\usetheme{Madrid}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}

\title{Examples and Analyses of Longitudinal Data}
\author{}
\date{}

\begin{document}

\frame{\titlepage}

\begin{frame}{What is Longitudinal Data?}
\begin{itemize}
    \item Repeated observations of the same variables over time.
    \item Tracks individuals, groups, or entities across multiple time points.
    \item Enables the study of changes, trends, and causal relationships.
\end{itemize}
\end{frame}

\begin{frame}{1. Health and Aging Studies}
\textbf{Data:}
\begin{itemize}
    \item Medical metrics, lifestyle habits, health outcomes.
\end{itemize}
\textbf{Elaborations:}
\begin{itemize}
    \item Model risk factors for chronic diseases.
    \item Estimate aging trajectories and disease onset.
    \item Discover health progression patterns.
\end{itemize}
\end{frame}

\begin{frame}{2. Student Performance Over Years}
\textbf{Data:}
\begin{itemize}
    \item Grades, attendance, behavior, socioeconomic background.
\end{itemize}
\textbf{Elaborations:}
\begin{itemize}
    \item Identify learning trajectories and at-risk students.
    \item Measure long-term intervention impacts.
    \item Model dropout probabilities.
\end{itemize}
\end{frame}

\begin{frame}{3. Social Media Behavior}
\textbf{Data:}
\begin{itemize}
    \item Posts, likes, topics, network connections over time.
\end{itemize}
\textbf{Elaborations:}
\begin{itemize}
    \item Track topic evolution and sentiment.
    \item Analyze user engagement patterns.
    \item Forecast content virality and user churn.
\end{itemize}
\end{frame}

\begin{frame}{4. Firm Financial Data}
\textbf{Data:}
\begin{itemize}
    \item Quarterly statements, stock prices, mergers.
\end{itemize}
\textbf{Elaborations:}
\begin{itemize}
    \item Predict revenue and financial distress.
    \item Perform panel data regression for policy impact.
    \item Cluster firms by risk or growth trajectories.
\end{itemize}
\end{frame}

\begin{frame}{5. Environmental Monitoring}
\textbf{Data:}
\begin{itemize}
    \item Pollution levels, weather data, traffic.
\end{itemize}
\textbf{Elaborations:}
\begin{itemize}
    \item Model seasonal patterns and anomalies.
    \item Perform spatiotemporal hotspot analysis.
    \item Link pollution to health data.
\end{itemize}
\end{frame}

\begin{frame}{6. E-Commerce Customer Behavior}
\textbf{Data:}
\begin{itemize}
    \item Purchase history, browsing, demographics.
\end{itemize}
\textbf{Elaborations:}
\begin{itemize}
    \item Predict customer lifetime value.
    \item Develop time-aware recommendation systems.
    \item Evaluate campaign effectiveness.
\end{itemize}
\end{frame}

\begin{frame}{7. Psychological and Psychiatric Studies}
\textbf{Data:}
\begin{itemize}
    \item Therapy records, medication, self-reports.
\end{itemize}
\textbf{Elaborations:}
\begin{itemize}
    \item Track symptom progression and relapse.
    \item Evaluate long-term treatment efficacy.
    \item Model dynamic psychological networks.
\end{itemize}
\end{frame}

\begin{frame}{Conclusion}
\begin{itemize}
    \item Longitudinal data unlocks rich insights into temporal dynamics.
    \item Applicable in health, education, finance, behavior, and more.
    \item Enables both predictive modeling and causal inference.
\end{itemize}
\end{frame}

\end{document}
